Preparing for Potential Closure of European Airspaces due to Re-entering Space Objects

### 2025-02-17 paper.qmd
shuffle files around

format:
  html: default
  ieee-pdf:
    keep-tex: true
    journaltype: conference
    papersize: a4
  ieee-html: default

@@

bibliography: references.bib

@@

We base our hourly flight density estimation on (enhanced) trajectories flown
by \acr{IFR} commercial aircraft as
recorded by EUROCONTROL's \acr{NM}[^1] and overlapped on Uber's H3
gridding system at different resolutions [@h3resolutions], see @fig-cells 
for resolution 2 which corresponds to hexagons of average area $86801.78\ km^2$
and average edge length of $182.51 km$.

@@

```{r cells-map}
#| out-width: "100%"
#| echo: false
knitr::include_graphics("figures/cells_2.png")
```

@@

```{r density-winter-res-2}
#| out-width: "100%"
#| echo: false
knitr::include_graphics("figures/flight_density_2024-08-01T12_2.png")
```

>>>>

format:
  ieee-pdf:
    keep-tex: true
    journaltype: conference
    papersize: a4
  ieee-html: default

@@

bibliography: media/references.bib

@@

We base our hourly flight density estimation on (enhanced) trajectories flown
by \acr{IFR} commercial aircraft as
recorded by EUROCONTROL's \acr{NM}[^1] and overlapped on Uber's H3
gridding system at different resolutions [@h3resolutions], see @fig-cells 
for resolution 2 which corresponds to hexagons of average area $86801.78\ km^2$
and average edge length of $182.51 km$, see also table

```{r}
library(tidyverse)
library(gt)
library(gtExtras)

tribble(
  ~resolution, ~hex_area, ~hex_edge,
  2L , 86801.780398997, 182.5129565,
  3L,  12393.434655088,  68.97922179,
  4L,   1770.347654491,  26.07175968

) |> 
  gt() |> 
   cols_label(
    resolution ~ "Resolution",
    tidyselect::ends_with("area") ~ "Density, {{*persons* km^-2}}",
    # hex_area ~ md("Cell Area ({km^2}})"),
    hex_edge ~ "Edge length ({km}})"
  ) |> 
    gt::tab_header(
    title = md("H3 Cell Statistics"),
    subtitle = md("average hexagons")
  ) |> 
  opt_align_table_header(align = "left")
```

@@

```{r cells-map}
#| out-width: "100%"
#| echo: false
knitr::include_graphics("media/figures/cells_2.png")
```

@@

```{r density-winter-res-2}
#| out-width: "100%"
#| echo: false
knitr::include_graphics("media/figures/flight_density_2024-08-01T12_2.png")
```
